We Are All Trying to Describe Something And We Don't Have the Words

### 2023-04-11 outputs/paper/paper.qmd
added more plots to the PDF

>>>>

I'm gonna fix the axis labels later

#| label: fig-quadvalence1
#| fig-cap: Valence and Energy Quadrant 
#| echo: false
#| warning: false

ggplot(data = df, aes(x = energy, y = valence)) + 
  geom_point(aes(color = as.factor(jack))) +
  geom_vline(xintercept = mean(df$energy), color = "gray") +
  geom_hline(yintercept = mean(df$valence), color = "gray") +
  annotate("text", x = mean(df$energy), y = max(df$valence), 
           label = "High Energy, High Valence") +
  annotate("text", x = mean(df$energy), y = min(df$valence), 
           label = "High Energy, Low Valence") +
  annotate("text", x = min(df$energy), y = mean(df$valence), 
           label = "Low Energy, High Valence") +
  annotate("text", x = max(df$energy), y = mean(df$valence), 
           label = "Low Energy, Low Valence")

#| label: fig-quadvalence2
#| fig-cap: Valence and Energy Quadrant
#| echo: false
#| warning: false

ggplot(data = df, aes(x = energy, y = valence)) + 
  geom_point(aes(color = artist_name)) +
  geom_vline(xintercept = mean(df$energy), color = "gray") +
  geom_hline(yintercept = mean(df$valence), color = "gray") +
  annotate("text", x = mean(df$energy), y = max(df$valence), 
           label = "High Energy, High Valence") +
  annotate("text", x = mean(df$energy), y = min(df$valence), 
           label = "High Energy, Low Valence") +
  annotate("text", x = min(df$energy), y = mean(df$valence), 
           label = "Low Energy, High Valence") +
  annotate("text", x = max(df$energy), y = mean(df$valence), 
           label = "Low Energy, Low Valence") 
```

#| label: fig-quaddanceability
#| fig-cap: Danceability and Energy Quadrant
#| echo: false
#| warning: false

ggplot(data = df, aes(x = energy, y = danceability)) + 
  geom_point(aes(color = artist_name)) +
  geom_vline(xintercept = mean(df$energy), color = "gray") +
  geom_hline(yintercept = mean(df$danceability), color = "gray") +
  annotate("text", x = mean(df$energy), y = max(df$danceability), 
           label = "High Energy, High Danceability") +
  annotate("text", x = mean(df$energy), y = min(df$danceability), 
           label = "High Energy, Low Danceability") +
  annotate("text", x = min(df$energy), y = mean(df$danceability), 
           label = "Low Energy, High Danceability") +
  annotate("text", x = max(df$energy), y = mean(df$danceability), 
           label = "Low Energy, Low Danceability")

#| label: fig-quaddanceability2
#| fig-cap: Danceability and Energy Quadrant
#| echo: false
#| warning: false

ggplot(data = df, aes(x = energy, y = danceability)) + 
  geom_point(aes(color = as.factor(jack))) +
  geom_vline(xintercept = mean(df$energy), color = "gray") +
  geom_hline(yintercept = mean(df$danceability), color = "gray") +
  annotate("text", x = mean(df$energy), y = max(df$danceability), 
           label = "High Energy, High Danceability") +
  annotate("text", x = mean(df$energy), y = min(df$danceability), 
           label = "High Energy, Low Danceability") +
  annotate("text", x = min(df$energy), y = mean(df$danceability), 
           label = "Low Energy, High Danceability") +
  annotate("text", x = max(df$energy), y = mean(df$danceability), 
           label = "Low Energy, Low Danceability")
